The Galactic Midplane is Not a Plane: Implications for dynamical analysis with {\em Gaia} data and beyond

### 2019-04-22 paper/ms.tex
Add intuition for Jz hist

\begin{figure}
\plotone{fig/schmactions_Jz_hist.pdf}
\caption{A histogram of the observed values in $J_z$ for the thick-disk orbit
assuming a $z$ offset of $100\,\pc$. One can see that if the observed $z$
values have a bias (from e.g. an incorrectly computed midplane), then the
induced error distribution in $J_z$ is decidedly non-Gaussian. Therefore, any
sort of error propagation must take this into account. We also plot one half
the 95\uth{} percentile minus the 5\uth{} percentile of each distribution as a
horizontal arrow anchored on the true $J_z$ value. We call this $\Delta J_z$
and will use it (along with the similarly defined $\Delta J_r$ and $\Delta
L_z$) to empirically describe the error distribution. We see that $\Delta J_z$
roughly corresponds to the distance from the true $J_z$ value to one of the
modes of the error distribution.}
\label{fig:Jz_hist}
\end{figure}

@@

>>>>

\begin{figure}
\plotone{fig/schmactions_Jz_hist.pdf}
\caption{A histogram of the observed values in $J_z$ for the thick-disk orbit
assuming a $z$ offset of $100\,\pc$. One can see that if the observed $z$
values have a bias (from e.g. an incorrectly computed midplane), then the
induced error distribution in $J_z$ is decidedly non-Gaussian. Therefore, any
sort of error propagation must take this into account. Intuition for the shape of each panel is given in the text. We also plot one half
the 95\uth{} percentile minus the 5\uth{} percentile of each distribution as a
horizontal arrow anchored on the true $J_z$ value. We call this $\Delta J_z$
and will use it (along with the similarly defined $\Delta J_r$ and $\Delta
L_z$) to empirically describe the error distribution. We see that $\Delta J_z$
roughly corresponds to the distance from the true $J_z$ value to one of the
modes of the error distribution.}
\label{fig:Jz_hist}
\end{figure}

@@

The intuition behind the shape of Figure~\ref{fig:Jz_hist} is relatively
simple. Consider first the thick-disk orbit ({\em top} panel), where the
offset in $z$ is much less than $z_{\text{max}}$ of the orbit. The peaks in
the distribution correspond to the turning points of the orbit (or points of
maximum vertical amplitude), where $\v_z \sim 0$ and where the star spends
most of it orbit. This is why the distribution is peaked on these values. For
the thin-disk orbit ({\em bottom} panel), the offset in $z$ is comparable to
$z_{\text{max}}$. Now, there will be some points in the orbit where $v_z = 0$
and $z=0$ (in the observed, erroneous coordinate system). At these points, the
computed $J_z$ will vanish. The asymmetry and systematic offset then comes
about because of the constraint that $J_z \geg 0$.\footnote{This is similar to
arguments in cosmology for why gravity produces non-Gaussianity in the density
field, since the density cannot become negative but it can grow arbitrarily
large.}
